%% {\em Complete the Research and Related Budget form in accordance with
%%   the instructions on the form (Activate Help Mode to see
%%   instructions) and the following instructions.  You must complete a
%%   separate budget for the support requested (one budget for the
%%   applicant and a budget for each subawardee).  The form will generate
%%   a cumulative budget for the total project period.  You must complete
%%   all the mandatory information on the form before the NEXT PERIOD
%%   button is activated.  You may request funds under any of the
%%   categories (other than ``Participant/Trainee Support Costs'') listed
%%   as long as the item and amount are necessary to perform the proposed
%%   work, meet all the criteria for allowability under the applicable
%%   Federal cost principles, and are not prohibited by the funding
%%   restrictions in this announcement (See PART IV, G).}
 
%\section{Budget Justification} %(Field K on the form). 

%% {\em Provide the required supporting information for all proposed
%%   costs (See R\&R Budget instructions.  Attach a single budget
%%   justification file (will not count in page limit) for the entire
%%   project period in Field K.  The file automatically carries over to
%%   each budget year.  Please note, if you are selected for an award,
%%   additional budget information will most likely be required.

%%   Notes regarding Budget:
  
%%   \begin{itemize}
%%     \item Although there is no absolute cap on indirect costs, grant
%%       applications will be evaluated for overall economy and value to
%%       DOE.

%%     \item Tuition expenses are only allowable if requested from a
%%       subcontractor that is a University and if the amount requested
%%       for tuition is reasonable and comparable to the amount a student
%%       would be paid for performing research during the grant period.

%%     \item Travel funds must be justified and directly related to the
%%       needs of the project.  Travel expenses for technical conferences
%%       are not permitted unless the purpose of attending the conference
%%       directly relates to the project (e.g., to present research
%%       results of the project).  Funds to cover travel expenses outside
%%       of the U.S. is considered an unallowable cost unless written
%%       approval has been obtained from the SBIR/STTR Program Manager.

%%      \item Grants may include a profit or fee for the small business.

%%      \item Any commercial and/or in-kind contribution to the project
%%        should be reflected in the project narrative and not included
%%        on the budget pages.
%% \end{itemize}
%% }

\section{Section A -- Senior/Key Personnel}
Dr. Ben O'Neill is the PI and will lead the technical effort with
assistance from Dr. Gerald Sabin and Truong Nguyen. Dr. Sabin will also assist Dr. O'Neill with the management aspects of the Phase II project. Rates and hours are included in the cost proposal. 

\section{Section B -- Other Personnel}
Pavan Yallamelli, Research Scientist, will assist with implementation and testing. 

\section{Section C -- Equipment Description (Items Exceeding \$5,000)}
No major equipment.

\section{Section D -- Travel}
There will be two meetings with the DOE Program Manager and interested
DOE scientists. The first will be a kick-off meeting (i.e., the DOE PI
Meeting) to start the contract and ensure that the DOE needs are
met. The second is a review meeting toward the end of the project to
discuss the project status.  RNET is not budgeting any cost for
travel. RNET travel expenses (e.g., if both meetings
are in person) will be paid from internal funding.

\section{Section E -- Participant/Trainee Support Costs}
None
  
  
\section{Section F -- Other Direct Costs}
\subsection{Subcontract}

Oakridge National Laboratory is subcontractor on this project. The ORNL budget
and a letter of commitment are attached to this proposal submission.

\section{Section H -- Indirect Costs}
RNET uses a labor overhead of 51\%. This overhead includes, fringe
benefits (holidays, sick leave, vacation, health-care benefits and
retirement contributions), payroll taxes, and other indirect charges.

RNET charges 7\% for ``General and Administrative'' tasks (G\&A),
including accounting, payroll services, office rent, office supplies,
telephone, Internet connection, etc.

\section{Section J -- Fee}
RNET charges a fee (profit) of slightly less than 7\%.  This fee is consistent with other accepted RNET contracts.

