 {{\underline{Education}}}

  \begin{itemize}
\setlength{\itemsep}{0.2pt}
  \item Wright State Univeristy (WSU), Dayton, OH
\begin{itemize}
\item Ph.D. in Computational Science and Mathematics, August 2019.
\end{itemize}
  \item California State University Northridge (CSUN), Northridge, CA
\begin{itemize}
\item M.S. in Applied Mathematics, August 2015.
\end{itemize}
	\item San Jose State Univeristy (SJSU), San Jose, CA
\begin{itemize}
\item Bachelor of Art in Mathematics, May 2011. 
\end{itemize}
  \end{itemize}
  
{ {\underline{Experiences}}}
  
\begin{itemize}
\setlength{\itemsep}{0.2pt}
  
\item Researcher, RNET Technologies, April 2019 - Present
\begin{itemize}
\item Tensor Contraction and Operation Minimization for Extreme Scale Computational Chemistry.
\end{itemize}
\item Computational Mechanics Intern, Applied Optimization, May 2018 - March 2019
\begin{itemize}
\item Development an in-house solver for the Nonlinear Thermal/Distortion Analysis of Materials.
\end{itemize}
\item Graduate Research Assistant, CSUN-WSU, April 2014-Present\\\
{\em Mentors: Alex Alekseenko (CSUN), Amit Sharma (WSU), Mohamed Sulman (WSU), Aihua Wood (AFIT)}
\begin{itemize}
\item Developing a fast deterministic-stochastic method for computing the Boltzmann’s collision operator in $O(MN)$ operations where N is the degree of freedom in the three dimensional velocity space and $M < N$ using a machine learning approach to estimate the Boltzmann's velocity distribution function as a Gaussian Mixtures Model.
\item Developing an efficient solver for numerical modeling of solutions to a system of nonlinear equations that capture the collapse phenomenon of plasma’s density in the Ionosphere layer of the Earth.
\item Developing a positivity preserving adaptive moving mesh finite element methods for nonlinear diffusion-reaction-chemotaxis systems of PDEs.
\end{itemize}
\end{itemize}
  
{ {\underline{Publications }}}
\begin{itemize}
\setlength{\itemsep}{0.2pt}
\item M. Sulman, T. Nguyen, A Positivity Preserving Moving Mesh Method for Cancer Invasion Model, J. Computational and Applied Math, (in review).
\item M. Sulman, T. Nguyen, A Positivity Preserving Moving Mesh Finite Element Method for the Keller-Segel Chemotaxis Model, J. Sci. Compt., (2019).
\item A. Alekseenko, T. Nguyen, A. Wood, A deterministic-stochastic method for computing the Boltzmann collision integral in $O(MN)$ operations, Kinetic \& Related Models, Vol 11, 2018.
\end{itemize}